Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2012-01-23 article.tex
Rewrote paragraph on spectral leakage
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1468 ccdd05d5-56c1-461a-bf98-85f6876523b4

Another way of stating Theorem~\ref{thm:nyquist-dual} is that, provided $x(t)$ vanishes for $|t| > t_M$, where $t_M < 1 / (2 \, \Delta f)$, the continuous Fourier transform can be reconstructed at any frequency $f$ from a weighted sum of $\sinc$ functions centered at each of the discrete frequency components, namely,
$$
	\tilde{x}(f) \propto \sum_{n=-\infty}^{\infty} \tilde{x}\left(n \, \Delta f\right) \sinc \left[ 2 \pi (f - n \, \Delta f) t_M \right].
$$
Failure to meet this dual of the Nyquist-Shannon sampling criterion means that power from one of the discrete frequency components will ``leak'' into the rest of the spectrum through the side lobes of the $\sinc$ functions, producing a smeared out version of the desired frequency response.  In the \GW\ data analysis literature, the synthesis of inspiral matched filters involves a step called \emph{inverse spectrum truncation} \citep[see][section VII]{findchirppaper} that fixes the number of coefficients based on the desired frequency resolution.

>>>>

Another way of stating Theorem~\ref{thm:nyquist-dual} is that, provided $x(t)$ is nonzero only for $|t| < 1 / (2 \, \Delta f)$, the continuous Fourier transform can be reconstructed at any frequency $f$ from a weighted sum of $\sinc$ functions centered at each of the discrete frequency components, namely,
$$
	\tilde{x}(f) \propto \sum_{n=-\infty}^{\infty} \tilde{x}\left(n \, \Delta f\right) \sinc \left[ \pi (f - n \, \Delta f) / \Delta f \right].
$$
Failure to meet the conditions of this dual of the sampling theorem results in spectral leakage.  For a time-domain signal to capture spectral features that are the size of the central lobe of the $\sinc$ function, the signal must have a duration greater than $1/\Delta f$.  If the signal $x(t)$ is truncated by sampling it for a shorter duration, then its Fourier transform becomes smeared out; conceptually, power ``leaks'' out into the side lobes of the $\sinc$ functions and washes away sharp spectral features.  In the \GW\ data analysis literature, the synthesis of inspiral matched filters involves a step called \emph{inverse spectrum truncation} \citep[see][section VII]{findchirppaper} that fixes the number of coefficients based on the desired frequency resolution.
